---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tomleditR (archived)

<!-- badges: start -->
[![codecov](https://codecov.io/gh/extendr/tomleditR/branch/main/graph/badge.svg?token=MNPMZPDPGY)](https://codecov.io/gh/extendr/tomleditR)
[![CRAN status](https://www.r-pkg.org/badges/version/tomleditR)](https://CRAN.R-project.org/package=tomleditR)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/extendr/tomleditR/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/extendr/tomleditR/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->


> [!WARNING]
> 
> `tomleditR` has been archived. Refer to [`tomledit`](https://github.com/extendr/tomledit) as the successor to `tomleditR`.

The goal of tomleditR is to expose the [toml_edit](https://docs.rs/toml_edit/latest/toml_edit/) crate to R.

## Installation

You can install the development version of tomleditR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("extendr/tomleditR")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example1}
tomleditR::inspect("")
```

Or you can take a peek at a specific value:

```{r example2}
tomleditR::get_value("[package]\nname = \"tomleditR\"\nversion = \"0.0.0\"\n", c("package", "version"))
```
